---
title: "Weston PD ANOVA Results"
author: "Daniel Palmer, PhD"
date: "October 31, 2017"
output: word_document
---

```{r echo=FALSE, message=FALSE, warning=FALSE}
#################################################
#                                               #
#                                               #
#         Weston Anova Script                   #
#        Pairwise Discrimination                #
#                                               #
#                                               #
#################################################

## Library ##
library(plyr)
#library(tidyverse)
library(reshape2)
library(car)

## Functions List ##

# Separate Into Strains for Analysis #
Strain.Separation.Function = function(dataset,long.form=0){
  new.data = list()
  if(long.form == 0){
    new.data$APP = dataset[which(dataset$Mouse.Strain=="APP-PS1"), c(2:9)]
    new.data$TG3x = dataset[which(dataset$Mouse.Strain=="3xTG-AD"), c(2:9)]
    new.data$TG5x = dataset[which(dataset$Mouse.Strain=="5xFAD"), c(2:9)] 
  }else if(long.form == 1){
    new.data$APP = dataset[which(dataset$Mouse.Strain=="APP-PS1"), c(2:11,15:18,49,81)]
    new.data$TG3x = dataset[which(dataset$Mouse.Strain=="3xTG-AD"), c(2:11,15:18,49,81)]
    new.data$TG5x = dataset[which(dataset$Mouse.Strain=="5xFAD"), c(2:11,15:18,49,81)]
  }
  return(new.data)
}

# Separate Into Separate Measures for Each File + Transform # #
Measure.Separation.Function = function(dataset, file.type=0){
  new.data = list()
  if(file.type == 1){
    new.data$APP$Sessions = dataset$APP[ ,c(1:8)]
    new.data$TG5x$Sessions = dataset$TG5x[ ,c(1:8)]
    new.data$TG3x$Sessions = dataset$TG3x[ ,c(1:8)]
  }else if(file.type == 2){
    new.data$APP$Sessions = dataset$APP[ ,c(1:8)]
    new.data$TG5x$Sessions = dataset$TG5x[ ,c(1:8)]
    new.data$TG3x$Sessions = dataset$TG3x[ ,c(1:8)]
  }else if(file.type == 3){
    new.data$APP$TotalTime = dataset$APP[ ,c(2:8,10,11)]
    new.data$APP$TotalTrials = dataset$APP[ ,c(2:8,10,12)]
    new.data$APP$Accuracy = dataset$APP[ ,c(2:8,10,14)]
    new.data$APP$Corrections = dataset$APP[ ,c(2:8,10,13)]
    new.data$APP$RewardLat = dataset$APP[ ,c(2:8,10,16)]
    new.data$APP$CorrectLat = dataset$APP[ ,c(2:8,10,15)]
    
    new.data$TG5x$TotalTime = dataset$TG5x[ ,c(2:8,10,11)]
    new.data$TG5x$TotalTrials = dataset$TG5x[ ,c(2:8,10,12)]
    new.data$TG5x$Accuracy = dataset$TG5x[ ,c(2:8,10,14)]
    new.data$TG5x$Corrections = dataset$TG5x[ ,c(2:8,10,13)]
    new.data$TG5x$RewardLat = dataset$TG5x[ ,c(2:8,10,16)]
    new.data$TG5x$CorrectLat = dataset$TG5x[ ,c(2:8,10,15)]
    
    new.data$TG3x$TotalTime = dataset$TG3x[ ,c(2:8,10,11)]
    new.data$TG3x$TotalTrials = dataset$TG3x[ ,c(2:8,10,12)]
    new.data$TG3x$Accuracy = dataset$TG3x[ ,c(2:8,10,14)]
    new.data$TG3x$Corrections = dataset$TG3x[ ,c(2:8,10,13)]
    new.data$TG3x$RewardLat = dataset$TG3x[ ,c(2:8,10,16)]
    new.data$TG3x$CorrectLat = dataset$TG3x[ ,c(2:8,10,15)]
  }
  return(new.data)
}

# Data Format - Long to Wide ##
Data.Formatting.Function = function(dataset,m.value,data.type){
  for(a in 1:3){
    for(b in 1:m.value){
      temp.data = as.data.frame(dataset[[a]][[b]])
      if(data.type == 3){
        colnames(temp.data)[9] = 'Value'
        temp.data = temp.data[which((temp.data$Task == 'PD Reversal 1') |(temp.data$Task == 'PD Reversal 2') | (temp.data$Task == 'PD Reversal 3')), ]
      }else{
        colnames(temp.data)[8] = 'Value' 
      }
      if(data.type == 1){
        data.cast = dcast(temp.data, AnimalID + TestSite + Mouse.Strain + Genotype + Sex ~ Age.Months + Task, fun.aggregate = mean, na.rm=TRUE, value.var="Value")
      }else if(data.type == 2){
        data.cast = dcast(temp.data, AnimalID + TestSite + Mouse.Strain + Genotype + Sex ~ Age.Months + Task, fun.aggregate = mean, na.rm=TRUE, value.var="Value")
      }else if(data.type == 3){
        data.cast = dcast(temp.data, AnimalID + TestSite + Mouse.Strain + Genotype + Sex ~ Age.Months + Task + Day, fun.aggregate = mean, na.rm=TRUE, value.var="Value")
      }
      for(c in 6:ncol(data.cast)){
        colnames(data.cast)[c] = paste('Data',colnames(data.cast)[c],sep=".")
      }
      dataset[[a]][[b]] = as.data.frame(data.cast)
    }
  }
  return(dataset)
}

# Generate iData for Repeated Measure Design (Probe Only) #
iData.Generate.Function = function(dataset){
  template.data = dataset[[1]][[1]]
  template.data = template.data[which((template.data$Task == 'PD Reversal 1') |(template.data$Task == 'PD Reversal 2') | (template.data$Task == 'PD Reversal 3')), ]
  idata = unique(template.data[c('Day')])
  idata = idata[order(idata), ]
  idata = as.factor(idata)
  return(idata)
}

# Calculate ANOVA Results #
Anova.Preparation.Main.Function = function(dataset,idata,age){
  for(a in 1:length(dataset)){
    for(b in 1:length(dataset[[a]])){
      data.file =dataset[[a]][[b]]
      data.file[ ,c(1,3)] = NULL
      if(age == 4){
        data.file = data.file[ ,c(1:3,4:13)]
        data.file = data.file[complete.cases(data.file), ]
        data.depend = data.file[ ,4:13]
        
      }else if(age == 7){
        data.file = data.file[ ,c(1:3,14:23)]
        data.file = data.file[complete.cases(data.file), ]
        data.depend = data.file[ ,4:13]
        
      }else if(age == 10){
        data.file = data.file[ ,c(1:3,24:33)]
        data.file = data.file[complete.cases(data.file), ]
        data.depend = data.file[ ,4:13]
      }
      data.lm = lm(as.matrix(data.depend) ~ 1 + Genotype * Sex, data=data.file)
      Day = as.data.frame(matrix(nrow=10,ncol=0))
      Day$Day = as.factor(idata)
      data.anova = Anova(data.lm, idata=Day,idesign=~Day, type="III")
      dataset[[a]][[b]] = data.anova
    }
  }
  return(dataset)
}

Anova.Preparation.Pretrain.Function = function(dataset){
  final.dataset = list()
  for(a in 1:length(dataset)){
    for(b in 1:length(dataset[[a]])){
      data.file =dataset[[a]][[b]]
      data.file = data.file[ ,c(4,5,9)]
      data.file = data.file[complete.cases(data.file), ]
      data.depend = data.file[ ,3]
      data.lm = lm(as.matrix(data.depend) ~ 1+ Genotype * Sex, data=data.file)
      data.anova = Anova(data.lm, type="III")
      dataset[[a]][[b]] = data.anova
    }
  }
  return(dataset)
}

Anova.Preparation.Acquisition.Function = function(dataset,age){
  final.dataset = list()
  for(a in 1:length(dataset)){
    for(b in 1:length(dataset[[a]])){
      data.file =dataset[[a]][[b]]
      data.file = data.file[complete.cases(data.file), ]
      data.file[ ,c(1:3)] = NULL
      if(age == 4){
        data.depend = data.file[ ,3]
      }else if(age == 7){
        data.depend = data.file[ ,4]
      }else if(age == 10){
        data.depend = data.file[ ,5]
      }
      data.lm = lm(as.matrix(data.depend) ~ 1+ Genotype * Sex, data=data.file)
      data.anova = Anova(data.lm, type="III")
      dataset[[a]][[b]] = data.anova
    }
  }
  return(dataset)
}

## Settings ##
options(scipen=50)
options(contrasts = c('contr.sum','contr.poly'))

## Read Data ##
#aw.data.pretrain = read.csv('C:\\Users\\dpalmer\\Documents\\WestonANOVAProcedure\\Data\\Raw\\5CSRTT\\Weston 5CSRTT Pretrain QC Oct 12 2017 Updated.csv')
#raw.data.acq = read.csv('C:\\Users\\dpalmer\\Documents\\WestonANOVAProcedure\\Data\\Raw\\5CSRTT\\Weston 5CSRTT Acquisition Aggregated QC Oct 12 2017 Updated.csv')
#raw.data.probe = read.csv('C:\\Users\\dpalmer\\Documents\\WestonANOVAProcedure\\Data\\Raw\\5CSRTT\\Weston 5CSRTT Probe Aggregated QC Oct 12 2017 Updated.csv')

#raw.data.pretrain = read.csv('C:\\Users\\Danie\\Documents\\R\\Projects\\Weston_R_Script\\Data\\Raw\\5CSRTT\\Weston 5CSRTT Pretrain QC Oct 12 2017 Updated.csv')
#raw.data.acq = read.csv('C:\\Users\\Danie\\Documents\\R\\Projects\\Weston_R_Script\\Data\\Raw\\5CSRTT\\Weston 5CSRTT Acquisition Aggregated QC Oct 12 2017 Updated.csv')
#raw.data.probe = read.csv('C:\\Users\\Danie\\Documents\\R\\Projects\\Weston_R_Script\\Data\\Raw\\5CSRTT\\Weston 5CSRTT Probe Aggregated QC Oct 12 2017 Updated.csv')

raw.data.pretrain = read.csv('C:\\Users\\dpalmer\\Documents\\Weston_R_Script\\Data\\Raw\\PD\\Weston PD Pretrain QC Oct 30 2017 Updated.csv')
raw.data.acq = read.csv('C:\\Users\\dpalmer\\Documents\\Weston_R_Script\\Data\\Raw\\PD\\Weston PD Acquisition Aggregated Oct 12 2017 Updated.csv')
raw.data.main = read.csv('C:\\Users\\dpalmer\\Documents\\Weston_R_Script\\Data\\Raw\\PD\\Weston PD Basline Reversal QC Oct 12 2017 Updated.csv')
raw.data.acq[ ,2] = NULL
## Separate each Raw File by Strain ##
pretrain.separated.data = Strain.Separation.Function(raw.data.pretrain,0)
acq.separated.data = Strain.Separation.Function(raw.data.acq,0)
main.separated.data = Strain.Separation.Function(raw.data.main,1)


## Separate Probe Data by Measure / Get Specific Columns ##
pretrain.separated.measures = Measure.Separation.Function(pretrain.separated.data,1)
acq.separated.measures = Measure.Separation.Function(acq.separated.data,2)
main.separated.measures = Measure.Separation.Function(main.separated.data,3)

## Remove Baseline Protocol From Main Task ##

## Format Data Long to Wide ##
pretrain.formatted.data = Data.Formatting.Function(pretrain.separated.measures,1,1)
acq.formatted.data = Data.Formatting.Function(acq.separated.measures,1,1)
main.formatted.data = Data.Formatting.Function(main.separated.measures,6,3)

## Gather iData for Repeated Measures ##
main.idata = iData.Generate.Function(main.separated.measures)

## Conduct ANOVA ##
pretrain.anova = Anova.Preparation.Pretrain.Function(pretrain.formatted.data)
acq.4month.anova = Anova.Preparation.Acquisition.Function(acq.formatted.data,4)
acq.7month.anova = Anova.Preparation.Acquisition.Function(acq.formatted.data,7)
acq.10month.anova = Anova.Preparation.Acquisition.Function(acq.formatted.data,10)
main.4month.anova = Anova.Preparation.Main.Function(main.formatted.data,main.idata,4)
main.7month.anova = Anova.Preparation.Main.Function(main.formatted.data,main.idata,7)
main.10month.anova = Anova.Preparation.Main.Function(main.formatted.data, main.idata, 10)

```


# Weston 5-CSRTT ANOVA Results Report
  This report details the standard univariate analyses of the Weston project data. The data used in this analysis represents the completed datasets obtained from the datafiles used for the spotfire website. 
  
## Pretraining - Punish Incorrect
### Number of Sessions
  This ANOVA was a 2 (Sex) x 2 (Genotype) x 2 (Test Site) design. 

#### APP/PS1 Mice
```{r}
pretrain.anova$APP$Sessions
```

#### 5xFAD Mice
```{r}
pretrain.anova$TG5x$Sessions
```

#### 3xTG Mice
```{r}
pretrain.anova$TG3x$Sessions
```

## Acquisition: 4 Months
### Number of Sessions
  This ANOVA was a 2 (Sex) x 2 (Genotype) design. 

#### APP/PS1 Mice
```{r}
acq.4month.anova$APP$Sessions
```

#### 5xFAD Mice
```{r}
acq.4month.anova$TG5x$Sessions
```

#### 3xTG Mice
```{r}
acq.4month.anova$TG3x$Sessions
```

## Acquisition: 7 Months
### Number of Sessions
  This ANOVA was a 2 (Sex) x 2 (Genotype) design. 

#### APP/PS1 Mice
```{r}
acq.7month.anova$APP$Sessions
```

#### 5xFAD Mice
```{r}
acq.7month.anova$TG5x$Sessions
```

#### 3xTG Mice
```{r}
acq.7month.anova$TG3x$Sessions
```

## Acquisition: 10 Months
### Number of Sessions
  This ANOVA was a 2 (Sex) x 2 (Genotype) design. 

#### APP/PS1 Mice
```{r}
acq.10month.anova$APP$Sessions
```

#### 5xFAD Mice
```{r}
acq.10month.anova$TG5x$Sessions
```

#### 3xTG Mice
```{r}
acq.10month.anova$TG3x$Sessions
```


## PAL Training Data: 4 Months
### Total Session Length
  This ANOVA was a 10 (Sessions) x 2 (Sex) x 2 (Genotype) Split-Plot design.

#### APP/PS1 Mice
```{r}
summary(main.4month.anova$APP$TotalTime, multivariate=FALSE)
```

#### 5xFAD Mice
```{r}
summary(main.4month.anova$TG5x$TotalTime, multivariate=FALSE)
```

#### 3xTG Mice
```{r}
summary(main.4month.anova$TG3x$TotalTime, multivariate=FALSE)
```

### Total Completed Trials
  This ANOVA was a 10 (Sessions) x 2 (Sex) x 2 (Genotype) Split-Plot design.

#### APP/PS1 Mice
```{r}
summary(main.4month.anova$APP$TotalTrials, multivariate=FALSE)
```

#### 5xFAD Mice
```{r}
summary(main.4month.anova$TG5x$TotalTrials, multivariate=FALSE)
```

#### 3xTG Mice
```{r}
summary(main.4month.anova$TG3x$TotalTrials, multivariate=FALSE)
```

### Session Accuracy
  This ANOVA was a 10 (Sessions) x 2 (Sex) x 2 (Genotype) Split-Plot design.

#### APP/PS1 Mice
```{r}
summary(main.4month.anova$APP$Accuracy, multivariate=FALSE)
```

#### 5xFAD Mice
```{r}
summary(main.4month.anova$TG5x$Accuracy, multivariate=FALSE)
```

#### 3xTG Mice
```{r}
summary(main.4month.anova$TG3x$Accuracy, multivariate=FALSE)
```

### Session Correction Trials
  This ANOVA was a 10 (Sessions) x 2 (Sex) x 2 (Genotype) Split-Plot design.

#### APP/PS1 Mice
```{r}
summary(main.4month.anova$APP$Corrections, multivariate=FALSE)
```

#### 5xFAD Mice
```{r}
summary(main.4month.anova$TG5x$Corrections, multivariate=FALSE)
```

#### 3xTG Mice
```{r}
summary(main.4month.anova$TG3x$Corrections, multivariate=FALSE)
```

### Correct Response Latency
  This ANOVA was a 10 (Sessions) x 2 (Sex) x 2 (Genotype) Split-Plot design.

#### APP/PS1 Mice
```{r}
summary(main.4month.anova$APP$CorrectLat, multivariate=FALSE)
```

#### 5xFAD Mice
```{r}
summary(main.4month.anova$TG5x$CorrectLat, multivariate=FALSE)
```

#### 3xTG Mice
```{r}
summary(main.4month.anova$TG3x$CorrectLat, multivariate=FALSE)
```

### Reward Collection Latency
  This ANOVA was a 10 (Sessions) x 2 (Sex) x 2 (Genotype) Split-Plot design.

#### APP/PS1 Mice
```{r}
summary(main.4month.anova$APP$RewardLat, multivariate=FALSE)
```

#### 5xFAD Mice
```{r}
summary(main.4month.anova$TG5x$RewardLat, multivariate=FALSE)
```

#### 3xTG Mice
```{r}
summary(main.4month.anova$TG3x$RewardLat, multivariate=FALSE)
```

## PAL Training Data: 7 Months
### Total Session Length
  This ANOVA was a 10 (Sessions) x 2 (Sex) x 2 (Genotype) Split-Plot design.

#### APP/PS1 Mice
```{r}
summary(main.7month.anova$APP$TotalTime, multivariate=FALSE)
```

#### 5xFAD Mice
```{r}
summary(main.7month.anova$TG5x$TotalTime, multivariate=FALSE)
```

#### 3xTG Mice
```{r}
summary(main.7month.anova$TG3x$TotalTime, multivariate=FALSE)
```

### Total Completed Trials
  This ANOVA was a 10 (Sessions) x 2 (Sex) x 2 (Genotype) Split-Plot design.

#### APP/PS1 Mice
```{r}
summary(main.7month.anova$APP$TotalTrials, multivariate=FALSE)
```

#### 5xFAD Mice
```{r}
summary(main.7month.anova$TG5x$TotalTrials, multivariate=FALSE)
```

#### 3xTG Mice
```{r}
summary(main.7month.anova$TG3x$TotalTrials, multivariate=FALSE)
```

### Session Accuracy
  This ANOVA was a 10 (Sessions) x 2 (Sex) x 2 (Genotype) Split-Plot design.

#### APP/PS1 Mice
```{r}
summary(main.7month.anova$APP$Accuracy, multivariate=FALSE)
```

#### 5xFAD Mice
```{r}
summary(main.7month.anova$TG5x$Accuracy, multivariate=FALSE)
```

#### 3xTG Mice
```{r}
summary(main.7month.anova$TG3x$Accuracy, multivariate=FALSE)
```

### Session Correction Trials
  This ANOVA was a 10 (Sessions) x 2 (Sex) x 2 (Genotype) Split-Plot design.

#### APP/PS1 Mice
```{r}
summary(main.7month.anova$APP$Corrections, multivariate=FALSE)
```

#### 5xFAD Mice
```{r}
summary(main.7month.anova$TG5x$Corrections, multivariate=FALSE)
```

#### 3xTG Mice
```{r}
summary(main.7month.anova$TG3x$Corrections, multivariate=FALSE)
```

### Correct Response Latency
  This ANOVA was a 10 (Sessions) x 2 (Sex) x 2 (Genotype) Split-Plot design.

#### APP/PS1 Mice
```{r}
summary(main.7month.anova$APP$CorrectLat, multivariate=FALSE)
```

#### 5xFAD Mice
```{r}
summary(main.7month.anova$TG5x$CorrectLat, multivariate=FALSE)
```

#### 3xTG Mice
```{r}
summary(main.7month.anova$TG3x$CorrectLat, multivariate=FALSE)
```

### Reward Collection Latency
  This ANOVA was a 10 (Sessions) x 2 (Sex) x 2 (Genotype) Split-Plot design.

#### APP/PS1 Mice
```{r}
summary(main.7month.anova$APP$RewardLat, multivariate=FALSE)
```

#### 5xFAD Mice
```{r}
summary(main.7month.anova$TG5x$RewardLat, multivariate=FALSE)
```

#### 3xTG Mice
```{r}
summary(main.7month.anova$TG3x$RewardLat, multivariate=FALSE)
```

## PAL Training Data: 10 Months
### Total Session Length
  This ANOVA was a 10 (Sessions) x 2 (Sex) x 2 (Genotype) Split-Plot design.

#### APP/PS1 Mice
```{r}
summary(main.10month.anova$APP$TotalTime, multivariate=FALSE)
```

#### 5xFAD Mice
```{r}
summary(main.10month.anova$TG5x$TotalTime, multivariate=FALSE)
```

#### 3xTG Mice
```{r}
summary(main.10month.anova$TG3x$TotalTime, multivariate=FALSE)
```

### Total Completed Trials
  This ANOVA was a 10 (Sessions) x 2 (Sex) x 2 (Genotype) Split-Plot design.

#### APP/PS1 Mice
```{r}
summary(main.10month.anova$APP$TotalTrials, multivariate=FALSE)
```

#### 5xFAD Mice
```{r}
summary(main.10month.anova$TG5x$TotalTrials, multivariate=FALSE)
```

#### 3xTG Mice
```{r}
summary(main.10month.anova$TG3x$TotalTrials, multivariate=FALSE)
```

### Session Accuracy
  This ANOVA was a 10 (Sessions) x 2 (Sex) x 2 (Genotype) Split-Plot design.

#### APP/PS1 Mice
```{r}
summary(main.10month.anova$APP$Accuracy, multivariate=FALSE)
```

#### 5xFAD Mice
```{r}
summary(main.10month.anova$TG5x$Accuracy, multivariate=FALSE)
```

#### 3xTG Mice
```{r}
summary(main.10month.anova$TG3x$Accuracy, multivariate=FALSE)
```

### Session Correction Trials
  This ANOVA was a 10 (Sessions) x 2 (Sex) x 2 (Genotype) Split-Plot design.

#### APP/PS1 Mice
```{r}
summary(main.10month.anova$APP$Corrections, multivariate=FALSE)
```

#### 5xFAD Mice
```{r}
summary(main.10month.anova$TG5x$Corrections, multivariate=FALSE)
```

#### 3xTG Mice
```{r}
summary(main.10month.anova$TG3x$Corrections, multivariate=FALSE)
```

### Correct Response Latency
  This ANOVA was a 10 (Sessions) x 2 (Sex) x 2 (Genotype) Split-Plot design.

#### APP/PS1 Mice
```{r}
summary(main.10month.anova$APP$CorrectLat, multivariate=FALSE)
```

#### 5xFAD Mice
```{r}
summary(main.10month.anova$TG5x$CorrectLat, multivariate=FALSE)
```

#### 3xTG Mice
```{r}
summary(main.10month.anova$TG3x$CorrectLat, multivariate=FALSE)
```

### Reward Collection Latency
  This ANOVA was a 10 (Sessions) x 2 (Sex) x 2 (Genotype) Split-Plot design.

#### APP/PS1 Mice
```{r}
summary(main.10month.anova$APP$RewardLat, multivariate=FALSE)
```

#### 5xFAD Mice
```{r}
summary(main.10month.anova$TG5x$RewardLat, multivariate=FALSE)
```

#### 3xTG Mice
```{r}
summary(main.10month.anova$TG3x$RewardLat, multivariate=FALSE)
```
